\chapter{Introduction}



\section{Company Profile}

At KCS, as a cloud and data solutions company with expertise on various technology
platforms, we enable our global customers to achieve digital transformation and provide
smart product solutions with our tech consulting, bespoke solutions, as well as
professional services. We enable clients across the globe to navigate their digital journey
with integrated technology models, business intelligence, and next-gen tech expertise to
catalyze change.
Our pragmatic approach to technology with agile methodologies helps deliver
unprecedented levels of solutions, service performances and customer delight. With
almost two decades of experience and more than 80% of referral business, we have
delivered with process discipline while following CMMI Level 5, ISO 27001 standards
and partnering with Microsoft Gold partner, Google cloud partner, Amazon cloud partner
as well as other OEMs

% Student write your company profile

\subsection{ Services Offered }
\subsubsection{International Consultancy}
We have been providing international consultancy from last 22 years and during we have established competitive foundation. Our consultancy Service consists of a highly skilled.

% This section type your project contents 


\subsubsection{Technical Consultancy}
Be it B2B, B2C or even B2E, KCS has driven service-centric project engagement models and have executed various end to end IT strategies including concept planning, architecture planning, project management, infrastructure planning, resource planning, applications development, database management, IT infrastructure planning and management, training as well as deployment. Our offerings include the
entire gamut from IT strategies to application development services.

% This section type your project contents 


\subsubsection{Web Development }
Today, the major increasing internal efficiencies and productivity through web services. We target that 

tools Our development team is well versed with the and technologies like- PHP, ASP .Net, Javascript, Ajax, React, NodeJs and Angular.

% This section type your project contents 

% This section type your project contents 
\subsubsection{Web Hosting }
The important and most overlooked aspect of site development is hosting. We offer reliable, secure and super-fast hosting services. We also provide hosting solutions.

% This section type your project contents 

\subsubsection{Software Development }
We are strong believers that the software you use for your business should be designed around.
% This section type your project contents  

\subsection{Clients and Products}
\begin{itemize} 


\item	Smart Town Mobile App. 
\item	eHospitality Services Management(eHSM) .
\item	H-Connect (Connecting Health Globally).
\item	\textbf{Digital India. }\\
          Website: http://www.kcsitglobal.com 
      
\end{itemize}




\section{Introduction To Digital India }
                             Digital India is a Web Application built using MERN (MongoDB, Express, React,
NodeJS) Stack. With Digital India you can register the electronic devices and control is
via Single Dashboard from anywhere.
It uses IoT Technology to achieve this functionality
                             .
\subsection{Need And Motivation}

% This section type your project contents 

\textbullet \hspace{0.2cm}The home automation market is primarily driven by growing need for effective solutions
in various domestic applications such as lighting, safety and security, energy
management, entertainment, and HVAC (heating, ventilation, and air conditioning).


\subsection{Problem Definition }
The project aims to design and construct a home automation system that Will remotely switch on or off any household appliances connected to it, using a microcontroller, voice dial on a phone, or Bluetooth/-based android application.
% This section type your project contents 

\subsection{Objective And Scope}
Considering the problem project is to develop Digitaly control Light,Fan,Tv etc. -  \textbf{Digital India}\\Application such that it overcomes the flaws of existing manual Switch. 
	 .\\
\textbullet \hspace{0.2cm}	\textbf{Device Owner}\\
o	Can add, update and delete new users and assign proper roles to them in the User concerned.  \\
o	User can  and to Add Device to Whitelist specific Command.\\

% This section type your project contents 

\subsection{Features of Proposed System}
Digital India systems involve making homes even smarter. Homes can be interfaced with sensors including motion sensors, light sensors and temperature sensors and provide
automated toggling of devices based on conditions.

\textbullet \hspace{0.2cm}Ability to control any registered device from a single dashboard.\\
\textbullet \hspace{0.2cm} Ability to register various type of devices that can be controlled later on using
commands \\
\textbullet \hspace{0.2cm}Ability to register different commands to control the registered devices \\
\textbullet \hspace{0.2cm} Ability to connect Google Assistant and Alexa to control the registered devices


% This section type your project contents 
