\chapter{Concluding Remarks}


\section{Strengths of System}

Smart home automation allows you to tap into hightech functionality and luxury that wasn’t possible in the past. As technology development continues to expand, so will the possibilities for consumer home automation to make life easier and more enjoyable.




% This section type your project contents 

\section{Limitations of system}

\begin{itemize}
\item  While the potential for remote device tampering is plenty scary, it pales in comparison with the risk of a physical break-in posed by security devices like
smart door locks and surveillance cameras.
\item  Not only do these digital voice assistants listen in on you continuously while on, but hackers can also exploit security loopholes to break into the speaker and issue their own commands or harvest prior recordings.
\item  The data transmitted by smart devices like printers and smart TVs are often unencrypted, a virtual villain can view—and alter—data collected by your devices.


% This section type your project contents 
\end{itemize}

\section{Scope for future development} 

In future we add User module and Client Module.
The next step would be to extend this system to automate a large-scale environment, such as offices and factories.
We will set timer for the module which you want to control automatically.
Sensors in smart homes will turn off utilities, close windows, monitor security,
and report to homeowners in real time.
The smart clock will scan your schedule and adjust the bussing time that you
will get ready for the tasks which you will going to perform.


% This section type your project contents 

\section{Conclusion}

\begin{itemize}
\item	igital India’s main purpose is to create a MERN application that helps Customers and other people use their home appliances remotely using their remotely held devices like Mobile phones, tablets, etc
\item	 The main motive of learning and acquiring the skills has also been achieved. \\
o	Way of analyzing the system.\\

% This section type your project contents 
o	Importance and skill of proper database design.\\
o	Proper use of state management tools.\\

% This section type your project contents 

\item	Company too is satisfied with the quality of work.

\end{itemize}