\thispagestyle{empty}
\begin{flushright}
\textit{\Large \textcolor{black} Abstract}\
\rule{6in}{.1pt}\\[0.5cm]
\end{flushright}
\justifying
\begin{spacing}{1.5}
Now a days, blind people can do more than anyone can Imagine. They can perform many computer applications, read textbooks and magazines, search on the Internet and send email. Some of the blind even can work as a clerk in office. Many different kinds of electronic devices are primarily designed for them in order to help them do whatever a normal person can do. The more popular and useful is the Braille display, which can display any text appearing on the computer to the blind user. Likewise Portable Braille Reader and Writer performs the job of reading and writing simultaneously. \\            
           This project will perform the functions such as  by using Braille keypad they can write any text and store the text into EEPROM. Also while writing it will provide sound of given text or word written. Text which has been written can be heard by blind user at any time. The document which is written can be uploaded on computer at any time using serial communication using RS232. Document which is present on computer can be uploaded on EPROM and can be heard at any time.\\                           
           There are many electronic models of Braille displays and writers available in markets. They all have one similarity, the cost. The price of the Braille displays in nowadays market is very high. These high costs are caused by two reasons, the invention of voice recognition and the smaller market size. Since the cost of the Braille displays is not affordable by many blind users, one of main goals is to build this device with low cost. Because this device  is built for a blind user, the focus of this project is to make the Braille unit and portable and user friendly.
\end{spacing}